### 2011-10-31 doc/theses/vitasek/chapter-4-1-experiments-setup.tex
Thesis: in progress.

We have implemented these ideas and incorporated them in the jInfer framework (see Appendix \ref{appedix-jInfer}). But before we describe the experiments themselves, we should try to formulate our aim.\\

@@

To interpret the data: \dataset{OVA*} sets have quite interesting and challenging graphs, but they are relatively small. We can consider them to be the ``typical" representants.

@@

This approach is useful, because as mentioned in Chapter \ref{chapter-research}, ID attributes are a special case of XML keys. We can use this approach to find XML keys: convert some ``suspicious" data into attributes, find the optimal ID set and then create XML key based on this ID set.

@@

The second, perhaps more interesting is $\frac{|E|}{E_{max}}$, where $E_{max} = \frac{|V|.(|V|-1)}{2}$. This is the density as the ratio of edges that are to all edges that could be in a complete graph with $|V|$ vertices.

@@

\begin{table}
  \caption{List of ``sized" artificial test data files}
  \bigskip
  \label{table-experiments-data-artificial-size}
  \centering
  \begin{tabular}{l | r | c | c | c | c | l}
	  Name  & Size [kb] & $|V|$ & $|E|$ & $\frac{|E|}{|V|}$ & $\frac{|E|}{E_{max}}$ & Optimum \\
  	\hline
  	\dataset{0-0}     & 0.2  & 0  & 0   & -    & -    & 0.0                \\
  	\dataset{10-5}    & 0.6  & 10 & 5   & 0.50 & 0.11 & 0.8500000000000002 \\
    \dataset{20-20}   & 1.7  & 18 & 13  & 0.72 & 0.08 & 0.7166666666666669 \\
    \dataset{30-45}   & 3.1  & 29 & 43  & 1.48 & 0.11 & 0.7083333333333334 \\
  	\dataset{40-80}   & 5.1  & 39 & 72  & 1.85 & 0.10 & 0.6950000000000002 \\
  	\dataset{50-125}  & 7.5  & 48 & 111 & 2.31 & 0.10 & 0.6566666666666666 \\
  	\dataset{60-180}  & 10.4 & 58 & 157 & 2.71 & 0.09 & 0.6214285714285716 \\
  	\dataset{70-245}  & 13.8 & 67 & 205 & 3.06 & 0.09 & 0.5982142857142856 \\
  	\dataset{80-320}  & 17.6 & 76 & 261 & 3.43 & 0.09 & 0.5791666666666667 \\
  	\dataset{90-405}  & 21.9 & 86 & 352 & 4.09 & 0.10 & 0.528888888888889  \\
  	\dataset{100-500} & 26.7 & 91 & 388 & 4.26 & 0.09 & 0.4981818181818182 \\
  \end{tabular}
\end{table}

\begin{figure}
  \caption{Artificial data}
  \label{image-experiments-data-artificial}
  \centering
  	\subfigure[\dataset{48-80}]{\includegraphics[width=\textwidth]{images/experiments/data/artificial/size/40-80}}
	\subfigure[\dataset{70-245}]{\includegraphics[width=.9\textwidth]{images/experiments/data/artificial/size/70-245-fixed}}
\end{figure}

@@

The ``user-specified limits" of whiskers are set to default value, let us quote from the manual again.

>>>>

We have implemented these ideas and incorporated them in the jInfer framework (see Appendix \ref{appendix-jInfer}). But before we describe the experiments themselves, we should try to formulate our aim.\\

@@

To interpret the data: \dataset{OVA*} sets have quite interesting and challenging graphs, but they are relatively small. We can consider them to be the ``typical'' representants.

@@

This approach is useful, because as mentioned in Chapter \ref{chapter-research}, ID attributes are a special case of XML keys. We can use this approach to find XML keys: convert some ``suspicious'' data into attributes, find the optimal ID set and then create XML key based on this ID set.

@@

The second, perhaps more interesting is $\frac{|E|}{E_{max}}$, where $E_{max} = \frac{|V|.(|V|-1)}{2}$. This is the density as the fraction of edges that are to all edges that could be in a complete graph with $|V|$ vertices.

@@

\begin{table}
  \caption{List of ``sized'' artificial test data files}
  \bigskip
  \label{table-experiments-data-artificial-size}
  \centering
  \begin{tabular}{l | r | c | c | c | c | l}
	  Name  & Size [kb] & $|V|$ & $|E|$ & $\frac{|E|}{|V|}$ & $\frac{|E|}{E_{max}}$ & Optimum \\
  	\hline
  	\dataset{0-0}     & 0.2  & 0  & 0   & -    & -    & 0.0                \\
  	\dataset{10-5}    & 0.6  & 10 & 5   & 0.50 & 0.11 & 0.8500000000000002 \\
    \dataset{20-20}   & 1.7  & 18 & 13  & 0.72 & 0.08 & 0.7166666666666669 \\
    \dataset{30-45}   & 3.1  & 29 & 43  & 1.48 & 0.11 & 0.7083333333333334 \\
  	\dataset{40-80}   & 5.1  & 39 & 72  & 1.85 & 0.10 & 0.6950000000000002 \\
  	\dataset{50-125}  & 7.5  & 48 & 111 & 2.31 & 0.10 & 0.6566666666666666 \\
  	\dataset{60-180}  & 10.4 & 58 & 157 & 2.71 & 0.09 & 0.6214285714285716 \\
  	\dataset{70-245}  & 13.8 & 67 & 205 & 3.06 & 0.09 & 0.5982142857142856 \\
  	\dataset{80-320}  & 17.6 & 76 & 261 & 3.43 & 0.09 & 0.5791666666666667 \\
  	\dataset{90-405}  & 21.9 & 86 & 352 & 4.09 & 0.10 & 0.528888888888889  \\
  	\dataset{100-500} & 26.7 & 91 & 388 & 4.26 & 0.09 & 0.4981818181818182 \\
  \end{tabular}
\end{table}

\begin{figure}
  \caption{Artificial data}
  \label{image-experiments-data-artificial}
  \centering
    \subfigure[\dataset{48-80}]{\includegraphics[width=\textwidth]{images/experiments/data/artificial/size/40-80}}
    \subfigure[\dataset{70-245}]{\includegraphics[width=.8\textwidth]{images/experiments/data/artificial/size/70-245-fixed}}
\end{figure}

@@

The ``user-specified limits'' of whiskers are set to default value, let us quote from the manual again.
